<!-- Page 1 : CI_Mas-Mas -->

Mas-Mas {data-navmenu="CI" data-icon="fa-circle-notch"}
=======================================================

Buttons {data-width=200}
-------------------------------------

### CI Mas-Mas {.value-box .no-title}

```{r}
valueBox("[pkg:Master] - [dep:Master]", color = "primary")

```

### GitHub Action {.value-box}

```{r}
valueBox("Trigger all bdverse pkgs",
         icon = "fa-circle-notch",
         href="https://github.com/bd-R/bdverse/actions",
         color = "info")

```

    
### CI Templates {.value-box}

```{r}
valueBox("CI Templates",
         icon = "fa-copy",
         href="https://github.com/tom-gu/bddummy/tree/master/.github/workflows",
         color = "success")

```



Triggered {data-width=400 .tabset .tabset-fade}
-------------------------------------
<center> <h4> User Triggered (Push & PR) </h4> </center>
   
### MacOs
<p class="text-muted"> Mac-latest; r-release</p>

<div>
#### bdutilities.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdutilities.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bddwc
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bddwc.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdchecks
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdchecks.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdclean
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>


<div>
#### bdverse
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>




### Windows

<p class="text-muted"> Win-latest; r-release</p>


<div>
#### bdutilities.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdutilities.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bddwc
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bddwc.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdchecks
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdchecks.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdclean
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>


<div>
#### bdverse
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>


### Ubuntu

<p class="text-muted"> Ubuntu-latest; r-release</p>

<div>
#### bdutilities.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdutilities.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bddwc
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bddwc.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdchecks
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdchecks.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdclean
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>


<div>
#### bdverse
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>



### Multi CI
<div>
#### bdutilities.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdutilities.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bddwc
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bddwc.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdchecks
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdchecks.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdclean
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>


<div>
#### bdverse
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>



### All

| Pkg | MacOs | Windows | Ubuntu | Multi-CI |
|----|---|---|---|---|
| `bdutilities` | ![mas-mas-ex](https://github.com/sunn-e/bddummy/workflows/mas-mas-ex/badge.svg)|![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg) | ![dev-dev-ex](https://github.com/sunn-e/bddummy/workflows/dev-dev-ex/badge.svg) | ![Level 0 CI](https://github.com/bd-R/bdverse/workflows/Level%200%20CI/badge.svg) |
| `bdutilities.app` | ![mas-mas-ex](https://github.com/sunn-e/bddummy/workflows/mas-mas-ex/badge.svg)|![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg) | ![dev-dev-ex](https://github.com/sunn-e/bddummy/workflows/dev-dev-ex/badge.svg) |  ![Level 0 CI](https://github.com/bd-R/bdverse/workflows/Level%200%20CI/badge.svg) |
| `bddwc` |![mas-mas-ex](https://github.com/sunn-e/bddummy/workflows/mas-mas-ex/badge.svg)|![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg) | ![dev-dev-ex](https://github.com/sunn-e/bddummy/workflows/dev-dev-ex/badge.svg) | ![Level 0 CI](https://github.com/bd-R/bdverse/workflows/Level%200%20CI/badge.svg) |
| `bddwc.app` | ![mas-mas-ex](https://github.com/sunn-e/bddummy/workflows/mas-mas-ex/badge.svg)|![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg) | ![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg) | ![Level 0 CI](https://github.com/bd-R/bdverse/workflows/Level%200%20CI/badge.svg) |
| `bdchecks` | ![mas-mas-ex](https://github.com/sunn-e/bddummy/workflows/mas-mas-ex/badge.svg)|![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg) | ![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg)  | ![Level 0 CI](https://github.com/bd-R/bdverse/workflows/Level%200%20CI/badge.svg) |
| `bdchecks.app` | ![mas-mas-ex](https://github.com/sunn-e/bddummy/workflows/mas-mas-ex/badge.svg)|![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg) | ![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg)  | ![Level 0 CI](https://github.com/bd-R/bdverse/workflows/Level%200%20CI/badge.svg) |
| `bdclean` | ![mas-mas-ex](https://github.com/sunn-e/bddummy/workflows/mas-mas-ex/badge.svg)|![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg) | ![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg)  | ![Level 0 CI](https://github.com/bd-R/bdverse/workflows/Level%200%20CI/badge.svg) |
| `bdverse` | ![mas-mas-ex](https://github.com/sunn-e/bddummy/workflows/mas-mas-ex/badge.svg)|![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg) | ![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg) | ![Level 0 CI](https://github.com/bd-R/bdverse/workflows/Level%200%20CI/badge.svg) |






   
Scheduled {data-width=400 .tabset .tabset-fade}
-------------------------------------
<center> <h4>Scheduled (Daily)</h4> </center>
   
### MacOs

<p class="text-muted"> Mac-latest; r-release</p>

<div>
#### bdutilities.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdutilities.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bddwc
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bddwc.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdchecks
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdchecks.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdclean
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>


<div>
#### bdverse
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>




### Windows

<p class="text-muted"> Win-latest; r-release</p>

<div>
#### bdutilities.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdutilities.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bddwc
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bddwc.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdchecks
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdchecks.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdclean
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>


<div>
#### bdverse
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>


### Ubuntu

<p class="text-muted"> Ubuntu-latest; r-release</p>

<div>
#### bdutilities.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdutilities.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bddwc
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bddwc.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdchecks
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdchecks.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdclean
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>


<div>
#### bdverse
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>



### Multi CI
<div>
#### bdutilities.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdutilities.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bddwc
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bddwc.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdchecks
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdchecks.app
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>

<div>
#### bdclean
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>


<div>
#### bdverse
```{r, out.width=params$badge_width, fig.align='left',  fig.link='https://github.com/sunn-e/bddummy/actions?query=workflow%3Amas-mas-ex+branch%3Amaster+event%3Apull_request+event%3Apush'}
knitr::include_graphics("https://github.com/bd-R/bdchecks/workflows/Level%201%20CI/badge.svg")
```
</div>





### All

| Pkg | MacOs | Windows | Ubuntu | Multi-CI |
|----|---|---|---|---|
| `bdutilities` | ![mas-mas-ex](https://github.com/sunn-e/bddummy/workflows/mas-mas-ex/badge.svg)|![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg) | ![dev-dev-ex](https://github.com/sunn-e/bddummy/workflows/dev-dev-ex/badge.svg) | ![Level 0 CI](https://github.com/bd-R/bdverse/workflows/Level%200%20CI/badge.svg) |
| `bdutilities.app` | ![mas-mas-ex](https://github.com/sunn-e/bddummy/workflows/mas-mas-ex/badge.svg)|![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg) | ![dev-dev-ex](https://github.com/sunn-e/bddummy/workflows/dev-dev-ex/badge.svg) |  ![Level 0 CI](https://github.com/bd-R/bdverse/workflows/Level%200%20CI/badge.svg) |
| `bddwc` |![mas-mas-ex](https://github.com/sunn-e/bddummy/workflows/mas-mas-ex/badge.svg)|![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg) | ![dev-dev-ex](https://github.com/sunn-e/bddummy/workflows/dev-dev-ex/badge.svg) | ![Level 0 CI](https://github.com/bd-R/bdverse/workflows/Level%200%20CI/badge.svg) |
| `bddwc.app` | ![mas-mas-ex](https://github.com/sunn-e/bddummy/workflows/mas-mas-ex/badge.svg)|![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg) | ![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg) | ![Level 0 CI](https://github.com/bd-R/bdverse/workflows/Level%200%20CI/badge.svg) |
| `bdchecks` | ![mas-mas-ex](https://github.com/sunn-e/bddummy/workflows/mas-mas-ex/badge.svg)|![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg) | ![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg)  | ![Level 0 CI](https://github.com/bd-R/bdverse/workflows/Level%200%20CI/badge.svg) |
| `bdchecks.app` | ![mas-mas-ex](https://github.com/sunn-e/bddummy/workflows/mas-mas-ex/badge.svg)|![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg) | ![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg)  | ![Level 0 CI](https://github.com/bd-R/bdverse/workflows/Level%200%20CI/badge.svg) |
| `bdclean` | ![mas-mas-ex](https://github.com/sunn-e/bddummy/workflows/mas-mas-ex/badge.svg)|![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg) | ![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg)  | ![Level 0 CI](https://github.com/bd-R/bdverse/workflows/Level%200%20CI/badge.svg) |
| `bdverse` | ![mas-mas-ex](https://github.com/sunn-e/bddummy/workflows/mas-mas-ex/badge.svg)|![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg) | ![dev-mas-ex](https://github.com/sunn-e/bddummy/workflows/dev-mas-ex/badge.svg) | ![Level 0 CI](https://github.com/bd-R/bdverse/workflows/Level%200%20CI/badge.svg) |